---
title: "Explorative data analysis github"
author: "Jonas Lieben"
date: "11/3/2016"
output: html_document
---

```{r setup, include=FALSE, cache=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(lubridate)
library(ggplot2)
library(gridExtra)
library(jsonlite)
library(httr)
library(tm)
library(stringr)

source("Extract_data_functions.R")
source("General_data_analysis.R")
source("Classify_commit_messages.R")
source("Calculate_right_beginning_timestamp.R")
```

```{r, cache=TRUE, include=FALSE}
#GitHub authentication data
username = "jonaslieben"
#do not forget to add a password
password = ""
```

```{r, cache=TRUE, include=FALSE}
#Github project data
owner = "apple"
repository = "swift-corelibs-foundation"
  
#set up the authentication 
authenticate <- authenticate(username,password)
```


```{r, cache=TRUE, include=FALSE}
# extract the event data from Github
eventData <- extractEventData(authenticate, owner, repository)
eventDataTable <- tbl_df(eventData)
```


```{r, cache=TRUE, include=FALSE}
# classify commit messages according to three categories
eventDataTable <- countAccordingToClassificationScheme(eventDataTable =  preprocessingNlp(eventData), classificationScheme = loadClassificationScheme())
eventDataTable <- classifyCommit(eventDataTable)

```

## Explorative data analysis

###Summary of the data
```{r, echo=FALSE, cache=TRUE}
summary(eventData)
```

###The amount of commits
```{r, echo=FALSE, cache=TRUE}
amountOfCommits(eventDataTable)
```
###Type of messages 
```{r, echo=FALSE, cache=TRUE}
eventDataTable %>% select(message, type) %>% group_by(type) %>% summarise(n = n())
```

###Amount of unique files currently in project
```{r, echo=FALSE, cache=TRUE}
amountOfFilesCurrrentlyInProject(eventDataTable)
```

###Amount of unique files which have been in the project
```{r, echo=FALSE, cache=TRUE}
amountOfFilesHaveBeenInProject(eventDataTable)
```


###Amount of people who contributed
```{r, echo=FALSE, cache=TRUE}
amountOfPeopleContributed(eventDataTable)
```

###Average amount of commits by one person
```{r, echo=FALSE, cache=TRUE}
averageCommitsPerPerson(eventDataTable)
```

###Max amount of commits by one person
```{r, echo=FALSE, cache=TRUE}
maxCommitsPerPerson(eventDataTable)
```

###Min amount of commits by one person
```{r, echo=FALSE, cache=TRUE}
minCommitsPerPerson(eventDataTable)
```

###Max amount of files changed by one person
```{r, echo=FALSE, cache=TRUE}
maxFilesChangedPerPerson(eventDataTable)
```

###Min amount of files changed by one person
```{r, echo=FALSE, cache=TRUE}
minFilesChangedPerPerson(eventDataTable)
```

###Average commits per day per person visualised in a density plot
```{r, echo=FALSE, cache=TRUE}
averageCommitsPerPersonPerDay(eventDataTable)
```

###Average commits per day per person visualised in a density plot without outliers (bigger than 2 SDs)
```{r, echo=FALSE, cache=TRUE}
averageCommitsPerPersonPerDayWithoutOutliers(eventDataTable)
```

###Highest average commits per day per person
```{r, echo=FALSE, cache=TRUE}
highestAverageCommitsPerPersonPerDay(eventDataTable)
```

###Mean average commits per day per person
```{r, echo=FALSE, cache=TRUE}
meanAverageCommitsPerPersonPerDay(eventDataTable)
```

###lowest average commits per day per person
```{r, echo=FALSE, cache=TRUE}
lowestAverageCommitsPerPersonPerDay(eventDataTable)
```

###Average commits per week per person visualised in a density plot
```{r, echo=FALSE, cache=TRUE}
averageCommitsPerPersonPerWeek(eventDataTable)
```

###Average commits per week per person visualised in a density plot without outliers (bigger than 2 SDs)
```{r, echo=FALSE, cache=TRUE}
averageCommitsPerPersonPerWeekWithoutOutliers(eventDataTable)
```

###Highest average commits per week per person
```{r, echo=FALSE, cache=TRUE}
highestAverageCommitsPerPersonPerWeek(eventDataTable)
```

###Mean average commits per week per person
```{r, echo=FALSE, cache=TRUE}
meanAverageCommitsPerPersonPerWeek(eventDataTable)
```

###lowest average commits per week per person
```{r, echo=FALSE, cache=TRUE}
lowestAverageCommitsPerPersonPerWeek(eventDataTable)
```

###Amount of files added, modified, removed and renamed 
```{r, echo=FALSE, cache=TRUE}
amountOfFileOperationsPerType(eventDataTable)
```

###Average amount of modification, additions, removes and renames per person
```{r, echo=FALSE, cache=TRUE}
averageAmountOfFilesOperationsPerTypePerPerson(eventDataTable)
```

###Max amount of modification, additions, removes and renames per person
```{r, echo=FALSE, cache=TRUE}
maxAmountOfFilesOperationsPerTypePerPerson(eventDataTable)
```

###Min amount of modification, additions, removes and renames per person
```{r, echo=FALSE, cache=TRUE}
minAmountOfFilesOperationsPerTypePerPerson(eventDataTable)
```

###Commit messages used more than once for a different commits
```{r, echo=FALSE, cache=TRUE}
commitMessagesUsedMoreThanOnce(eventDataTable)
```

###Author of commits with the same message
```{r, echo=FALSE, cache=TRUE}
AuthorOfCommitsWithMessagesUsedMoreThanOnce(eventDataTable)
```

###Ten most modified files
```{r, echo=FALSE, cache=TRUE}
tenMostModifiedFiles(eventDataTable)
```

###Ten most active people in terms of commits
```{r, echo=FALSE, cache=TRUE}
tenMostActivePeopleOnCommits(eventDataTable)
```

###Ten most active people in terms of files changed, added, removed and renamed
```{r, echo=FALSE, cache=TRUE}
tenMostActivePeopleOnFileOperations(eventDataTable)
```

###The number of different files on which the ten most active people work 
```{r, echo=FALSE, cache=TRUE}
numberFilesTenMostActivePeople(eventDataTable)
```

###Average amount of files per commit by dividing the amount of unique files with the commits
```{r, echo=FALSE, cache=TRUE}
averageFilesPerCommit(eventDataTable)
```

###Average amount of files per commit by looking on average how many files are changed per commit
```{r, echo=FALSE, cache=TRUE}
averageFilesPerCommitByCounting(eventDataTable)
```


###Average amount of file changes (added/modified/removed) per person
```{r, echo=FALSE, cache=TRUE}
averageFilesPerPerson(eventDataTable)
```

###Commits over time per month
```{r, echo=FALSE, cache=TRUE}
commitsOverTime(eventDataTable)
```

###Files changes/added/deleted over time
```{r, echo=FALSE, cache=TRUE}
fileOperationsOverTime(eventDataTable)
```

###Amount of active users over time
```{r, echo=FALSE, cache=TRUE}
amountOfActiveUsers(eventDataTable)
```

